Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-28 paper.qmd
Updated Figure 9

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 9

@@

@@

```{r}
#| label: hexbin-regular-two-curvy2
## hexagon binning to have regular hexagons
hb_obj_two_curvy2 <- hex_binning(
  data = umap_two_curvy_scaled, 
  bin1 = 12, 
  r2 = r2)

a1_2 <- calc_bins_y(
  bin1 = 12, 
  r2 = r2
  )$a1

@@

```{r}
#| label: hexbin-regular-two-curvy3
## hexagon binning to have regular hexagons
hb_obj_two_curvy3 <- hex_binning(
  data = umap_two_curvy_scaled, 
  bin1 = 14, 
  r2 = r2)

a1_3 <- calc_bins_y(
  bin1 = 14, 
  r2 = r2
)$a1

@@

# Compute radius r
a1 <- calc_bins_y(
  bin1 = 9, 
  r2 = r2, 
  q = 0.1)$a1

@@

mse_two_curvy_b <- ggplot(error_two_curvy_clust_umap, 
                     aes(x = a1, 
                         y = MSE)) +
  geom_vline(xintercept = 0.10, linetype=2,
           color = "#54278f", linewidth=1) +
  geom_vline(xintercept = 0.12,
             linetype="solid",
             color = "#006d2c",
             linewidth=1) +
  geom_vline(xintercept = 0.18, linetype=2,
             color = "#08519c", linewidth=1) +
  geom_line(linewidth = 0.5) + 
  geom_point(size = 1) +
  scale_x_continuous(breaks = sort(unique(round(error_two_curvy_clust_umap$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = "MSE") +
  ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

prop_dens_a1 <- ggplot(error_two_curvy_clust_umap,
                     aes(x = a1,
                         y = prop_comp)) +
  geom_vline(xintercept = 0.12, linetype="solid",
             color = "#006d2c", linewidth=1) +
  geom_vline(xintercept = 0.10, linetype=2,
             color = "#54278f", linewidth=1) +
  geom_vline(xintercept = 0.18, linetype=2,
             color = "#08519c", linewidth=1) +
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) +
  # scale_y_continuous(breaks = sort(unique(error_two_curvy$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_two_curvy_clust_umap$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = paste("proportion of densities")) +
  ggtitle("(d)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

>>>>

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 10

@@

a1_1 <- hb_obj_two_curvy$a1

@@

```{r}
#| label: hexbin-regular-two-curvy2
## hexagon binning to have regular hexagons
hb_obj_two_curvy2 <- hex_binning(
  data = umap_two_curvy_scaled, 
  bin1 = 14, 
  r2 = r2)

a1_2 <- calc_bins_y(
  bin1 = 14, 
  r2 = r2
  )$a1

@@

```{r}
#| label: hexbin-regular-two-curvy3
## hexagon binning to have regular hexagons
hb_obj_two_curvy3 <- hex_binning(
  data = umap_two_curvy_scaled, 
  bin1 = 17, 
  r2 = r2)

a1_3 <- calc_bins_y(
  bin1 = 17, 
  r2 = r2
)$a1

@@

# Compute radius r
a1 <- calc_bins_y(
  bin1 = 10, 
  r2 = r2, 
  q = 0.1)$a1

@@

mse_two_curvy_b <- ggplot(error_two_curvy_clust_umap, 
                     aes(x = a1, 
                         y = MSE)) +
  geom_vline(xintercept = 0.06,
             linetype="solid",
           color = "#54278f", linewidth=1) +
  geom_vline(xintercept = 0.04,
             color = "#006d2c", linetype=2,
             linewidth=1) +
  geom_vline(xintercept = 0.12, linetype=2,
             color = "#08519c", linewidth=1) +
  geom_line(linewidth = 0.5) + 
  geom_point(size = 1) +
  # scale_x_continuous(breaks = sort(unique(round(error_two_curvy_clust_umap$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = "MSE") +
  ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

prop_dens_a1 <- ggplot(error_two_curvy_clust_umap,
                     aes(x = a1,
                         y = prop_comp)) +
  geom_vline(xintercept = 0.06,
             linetype="solid",
           color = "#54278f", linewidth=1) +
  geom_vline(xintercept = 0.04,
             color = "#006d2c", linetype=2,
             linewidth=1) +
  geom_vline(xintercept = 0.12, linetype=2,
             color = "#08519c", linewidth=1) +
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) +
  # scale_y_continuous(breaks = sort(unique(error_two_curvy$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_two_curvy_clust_umap$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = paste("proportion of densities")) +
  ggtitle("(d)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())
